\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-29 paper.tex
update anonymization

\author{
         Ben Upenieks, Chaitanya Varier,\\
         Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
         Nicholas Geofroy, Chengzhong Meng, Vincent-Olivier Roch\\
         University of Waterloo\\
         \\
         \tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
         \\ \tt\small cdkphan@uwaterloo.ca, jdrwilli@uwaterloo.ca,
         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca
}

@@

Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving. However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets. Currently, this type of data is often created through computer generated scenarios due to the dangerous and costly nature of road collisions and data collection equipment. We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories. We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region. Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.

@@

In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems.
Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that might not be effectively simulated. 
This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
We propose that this egocentric dashcam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.

In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dashcam videos from various online video repositories to produce datasets that can be used to train deep dashcam collision prediction models.
We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
These datasets will also be collision-oriented as the majority of these videos contain collisions for people's viewing.
Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
This is the data we hope to capture by taking advantage of existing videos of non-artificial collisions.

The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
We use this data, in combination with the manually annotated data in order to create the collision dataset.
This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
As part of this data, we identify participants and bystanders, both known as agents. Participants are objects that are involved in a collision identified in the metadata, while bystanders are uninvolved objects.

@@

%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box.

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}": String that represents the type of the video
  \item "\texttt{url}": Url that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

@@

\item Web interface: Having a web-based user interface would be advantageous for this project. While currently being used in the context of (near-)collision, this software has the potential to become a platform for scraping automation and collaboration. Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.

>>>>

\author{
         Ben Upenieks, Chaitanya Varier,\\
         Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
         Nicholas Geofroy, Tony Meng, Vincent-Olivier Roch\\
         University of Waterloo\\
         \\
         \tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
         \\ \tt\small cdkphan@uwaterloo.ca, jdrwilli@uwaterloo.ca,
         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca
}

@@

The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing. Over the
last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving. However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets. Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions. We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods. Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.

@@

In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems.
Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
However, we can collect collision data naturally in real driving scenarios through the use of dash-cams - cheap video cameras that can be mounted to a car's dashboard.
Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.

In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dash-cam videos from various online video repositories to produce datasets that can be used to train deep dash-cam collision prediction models.
We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
These datasets will also be collision-oriented as the majority of these videos contain collisions for people's viewing.
Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
This is the data we hope to capture by taking advantage of existing videos of non-artificial collisions.

The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
We use this data, in combination with the manually annotated data in order to create the collision dataset.
This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
As part of this data, we identify participants and bystanders, both known as agents. Participants are objects that are involved in a collision identified in the metadata, while bystanders are objects that are not.

@@

%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box. We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}" is a string that represents the type of the video
  \item "\texttt{url}" is the url that the video was fetched from
  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
  \begin{itemize}
    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}`

@@

\item Web interface: Having a web-based user interface would be advantageous for this project. While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration. Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
